%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Project Experience}


%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}

%---------------------------------------------------------
  \cventry
    {Deep Learning Research Project} % Role / Project type
    {Deep Learning for Precipitation Nowcasting} % Project
    {} % Location
    {Feb. 2026 - Present} % Date(s)
    {
      \begin{cvitems} % Description(s)
        \item {Enhanced the SEVIR dataset with NASADEM-derived elevation, slope, aspect, and land-sea information.}
        \item {Built geospatial preprocessing foundations for future multi-source data fusion in precipitation nowcasting models.}
        \item {Prepared terrain-aware auxiliary inputs to support downstream deep learning experiments for short-term precipitation forecasting.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {LLM Fine-tuning Project} % Role / Project type
    {Fine-tuning Qwen3-0.6B-Base on Nemotron-CC-Math} % Project
    {} % Location
    {Mar. 2026 - May. 2026} % Date(s)
    {
      \begin{cvitems} % Description(s)
        \item {Fine-tuned Qwen3-0.6B-Base on Nemotron-CC-Math for mathematical domain adaptation.}
        \item {Designed a data cleaning pipeline using only regular expressions and Qwen3 itself, without teacher models, tool-calling, search, or external tools.}
        \item {Focused on lightweight, self-contained data filtering and refinement to support reproducible LLM post-training experiments.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Image Segmentation Project} % Role / Project type
    {Intelligent Scissors Project} % Project
    {} % Location
    {Apr. 2025 - May. 2025} % Date(s)
    {
      \begin{cvitems} % Description(s)
        \item {Implemented an interactive image segmentation system combining gradient-based edge detection with dynamic pathfinding.}
        \item {Applied Sobel operators to compute directional gradients and construct a weighted graph, assigning lower edge costs to stronger image boundaries.}
        \item {Used Dijkstra's algorithm for real-time optimal path calculation between user-selected points, with adaptive path stabilization and cursor snapping to maximum-gradient edges within a 5-pixel radius.}
      \end{cvitems}
    }

%---------------------------------------------------------
\end{cventries}
