%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Extracurricular Activity}


%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}

%---------------------------------------------------------
  \cventry
    {Summer Program Participant} % Affiliation/role
    {GEM Trailblazer Summer, Nanyang Technological University} % Organization/group
    {Singapore} % Location
    {Jun. 2024 - Jul. 2024} % Date(s)
    {
      \begin{cvitems} % Description(s)
        \item {Completed coursework in Cities and Urban Life and Introduction to Data Science \& Artificial Intelligence.}
        \item {Collaborated and built connections with peers from diverse educational and cultural backgrounds.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Starting Setter} % Affiliation/role
    {SUSTech Volleyball Team} % Organization/group
    {Shenzhen, China} % Location
    {May 2024 - Now} % Date(s)
    {
      \begin{cvitems} % Description(s)
        \item {Served as the starting setter for the Southern University of Science and Technology varsity volleyball team.}
        \item {Competed in the 14th Guangdong University Volleyball League, the 15th Guangdong Volleyball Championship, and the Shenzhen Intercollegiate Sports Competition volleyball event (third place).}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {President \& Undergraduate Captain} % Affiliation/role
    {SUSTech Volleyball Club \& Varsity Volleyball Team} % Organization/group
    {Shenzhen, China} % Location
    {Sept. 2025 - Aug. 2026} % Date(s)
    {
      \begin{cvitems} % Description(s)
        \item {Led the SUSTech Volleyball Club as president and served as undergraduate captain of the varsity volleyball team.}
      \end{cvitems}
    }

%---------------------------------------------------------
\end{cventries}
